---
title: '2D Pooling: Simulation'
author: "Xianbin Cheng"
date: "January 23, 2019"
output: html_document
---

# Objective  

  1. We want to simulate two-dimensional pooling.
  2. We want to analyze the performance and the cost.
  
# Method  

1. Load necessary libraries and files.  

```{r, message=FALSE, warning = FALSE}
library(tidyverse)
library(Hmisc)
library(mc2d)
source("1D_pooling_simulation.R")
source("2D_pooling_simulation.R")
source("STD_simulation.R")
```

2. Set input parameters

  * `n` = the total number of kernels in a plate (48 by default).
  * `thresh` = aflatoxin threshold

```{r}
#n = 48
#n_pos_vals = 1:47
thresh = 20
n_iter = 1000
```

3. Generate simulated data. Calculate sensitivity, specificity, and the total number of tests needed. The function used to generate random contamination levels is the same as the one used to generate data for STD simulation. 

```{r, eval = FALSE}
# sample size = 48
set.seed(123)
result_48 = tune_2d_n_pos(n_pos_vals = 1:(48-1), n_iter = n_iter, n = 48, thresh = thresh)
saveRDS(object = result_48, file = "2D_48_1000.rds")

# sample size = 96
set.seed(123)
result_96 = tune_2d_n_pos(n_pos_vals = 1:(96-1), n_iter = n_iter, n = 96, thresh = thresh)
saveRDS(object = result_96, file = "2D_96_1000.rds")
```

```{r, echo = FALSE}
result_48 = readRDS("2D_48_1000.rds")
result_96 = readRDS("2D_96_1000.rds")
```

```{r}
# 48-well
metrics_48 = do.call(what = rbind.data.frame, args = result_48) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_48 = calc_2d_cost(data = result_48, n = 48)

# 96-well
metrics_96 = do.call(what = rbind.data.frame, args = result_96) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_96 = calc_2d_cost(data = result_96, n = 96)
```

# Results

1. Visualization of metrics with simulated data.

```{r}
# 48-well
draw_metrics(df = metrics_48, n = 48, method = "median_hilow")

# 96-well
draw_metrics(df = metrics_96, n = 96, method = "median_hilow")
```

2. Cost analysis.

  1) The total number of tests needed:

```{r}
# 48-well
draw_cost(df = cost_48, n = 48, var = n_test_total, ylab = "The total number of tests needed")

# 96-well
draw_cost(df = cost_96, n = 96, var = n_test_total, ylab = "The total number of tests needed")
```

  2) The number of pipetting:
  
```{r}
# 48-well
draw_cost(df = cost_48, n = 48, var = n_pipette, ylab = "The number of transfers")

# 96-well
draw_cost(df = cost_96, n = 96, var = n_pipette, ylab = "The number of transfers")
```