---
title: 'Pooling: Visualization 3'
author: "Xianbin Cheng"
date: "February 16, 2019"
output: html_document
---

# Objective

Visualize the metrics for 48- and 96-well plate scenarios under the assumptions that healthy kernels follow modified PERT(0, 0.7, 19.99, 80) and contaminated kernels follow Gamma(2, mode = 40000).

# Method

1. Load all the necessary packages and source codes.

```{r, message=FALSE, warning = FALSE}
library(tidyverse)
library(Hmisc)
source("1D_pooling_simulation.R")
source("2D_pooling_simulation.R")
source("STD_simulation.R")
```

2. Read rds files and necessary parameters.

  * These files contain simulation results of STD(48; 7; 2) pooling, STD(96; 5; 3), one-dimensional and two-dimensional poolings. The iteration time is 1000. The seed is set at 123.

```{r, eval = FALSE}
# 48-well
STD_48 = readRDS(file = "STD_48_7_2_10000.rds")
pool_row_48 = readRDS("1D_row_48_10000.rds")
pool_col_48 = readRDS("1D_col_48_10000.rds")
pool_2d_48 = readRDS("2D_48_10000.rds")
STD_scheme_48 = read.csv("STD_48_7_2_1pos.csv", header = TRUE, row.names = 1)

# 96-well
STD_96 = readRDS(file = "STD_96_5_3_10000.rds")
pool_row_96 = readRDS("1D_row_96_10000.rds")
pool_col_96 = readRDS("1D_col_96_10000.rds")
pool_2d_96 = readRDS("2D_96_10000.rds")
STD_scheme_96 = read.csv("STD_96_5_3_1pos.csv", header = TRUE, row.names = 1)
```

3. Clean them up for visualization.

```{r, eval= FALSE}
### STD
# 48-well
metrics_STD_48 = do.call(what = rbind.data.frame, args = STD_48) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_STD_48 = calc_STD_cost(data = STD_48, n = 48, scheme = STD_scheme_48)

# 96-well
metrics_STD_96 = do.call(what = rbind.data.frame, args = STD_96) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_STD_96 = calc_STD_cost(data = STD_96, n = 96, scheme = STD_scheme_96)
```

```{r, eval= FALSE}
### 48-well
# Pool by rows
metrics_row_48 = do.call(what = rbind.data.frame, args = pool_row_48) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_row_48 = calc_1d_cost(data = pool_row_48, n = 48, by = "row")

# Pool by columns
metrics_col_48 = do.call(what = rbind.data.frame, args = pool_col_48) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_col_48 = calc_1d_cost(data = pool_col_48, n = 48, by = "column")

### 96-well
# Pool by rows
metrics_row_96 = do.call(what = rbind.data.frame, args = pool_row_96) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_row_96 = calc_1d_cost(data = pool_row_96, n = 96, by = "row")

# Pool by columns
metrics_col_96 = do.call(what = rbind.data.frame, args = pool_col_96) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_col_96 = calc_1d_cost(data = pool_col_96, n = 96, by = "column")
```

```{r, eval = FALSE}
## 2D Pool
# 48-well
metrics_2d_48 = do.call(what = rbind.data.frame, args = pool_2d_48) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_2d_48 = calc_2d_cost(data = pool_2d_48, n = 48)

# 96-well
metrics_2d_96 = do.call(what = rbind.data.frame, args = pool_2d_96) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
cost_2d_96 = calc_2d_cost(data = pool_2d_96, n = 96)
```

```{r, eval= FALSE}
#### 48-well
### All metrics
metrics_all_48 = bind_rows(metrics_STD_48, metrics_row_48, metrics_col_48, metrics_2d_48) %>%
  mutate(Pooling = c(rep("STD", times = nrow(metrics_STD_48)),
                     rep("Row", times = nrow(metrics_row_48)),
                     rep("Column", times = nrow(metrics_col_48)),
                     rep("2D", times = nrow(metrics_2d_48))))

### All cost
cost_all_48 = bind_rows(cost_STD_48, cost_row_48, cost_col_48, cost_2d_48) %>%
  mutate(Pooling = c(rep("STD", times = nrow(cost_STD_48)),
                     rep("Row", times = nrow(cost_row_48)),
                     rep("Column", times = nrow(cost_col_48)),
                     rep("2D", times = nrow(cost_2d_48))))

### 96-well
### All metrics
metrics_all_96 = bind_rows(metrics_STD_96, metrics_row_96, metrics_col_96, metrics_2d_96) %>%
  mutate(Pooling = c(rep("STD", times = nrow(metrics_STD_96)),
                     rep("Row", times = nrow(metrics_row_96)),
                     rep("Column", times = nrow(metrics_col_96)),
                     rep("2D", times = nrow(metrics_2d_96))))

### All cost
cost_all_96 = bind_rows(cost_STD_96, cost_row_96, cost_col_96, cost_2d_96) %>%
  mutate(Pooling = c(rep("STD", times = nrow(cost_STD_96)),
                     rep("Row", times = nrow(cost_row_96)),
                     rep("Column", times = nrow(cost_col_96)),
                     rep("2D", times = nrow(cost_2d_96))))
```

```{r, eval= FALSE}
write.csv(x = metrics_all_48, file = "Metrics_all_48_02_16_19.csv")
write.csv(x = metrics_all_96, file = "Metrics_all_96_02_16_19.csv")
write.csv(x = cost_all_48, file = "Cost_all_48_02_16_19.csv")
write.csv(x = cost_all_96, file = "Cost_all_96_02_16_19.csv")
```

```{r, echo= FALSE}
fix_levels = function(data){
  data$Pooling = factor(x = data$Pooling, levels = c("Column", "Row", "2D","STD")) 
  levels(data$Pooling) = c("1D: Column", "1D: Row", "2D", "STD")
  return(data)
}

metrics_all_48 = read.csv(file = "Metrics_all_48_02_10_19.csv", row.names = 1) %>% fix_levels(.)
metrics_all_96 = read.csv(file = "Metrics_all_96_02_10_19.csv", row.names = 1) %>% fix_levels(.)
cost_all_48 = read.csv(file = "Cost_all_48_02_10_19.csv", row.names = 1) %>% fix_levels(.)
cost_all_96 = read.csv(file = "Cost_all_96_02_10_19.csv", row.names = 1) %>% fix_levels(.)
```

# Result

1. Visualization of metrics

```{r, fig.show = "hold", out.width = "50%"}
# 48-well
p1 = draw_metrics_all(df = metrics_all_48, n = 48, ylab = "Metric values (48-well plate)")
p1

# 96-well
p2 = draw_metrics_all(df = metrics_all_96, n = 96, ylab = "Metric values (96-well plate)")
p2
```

2. Visualization of reagent cost.

```{r, fig.show = "hold", out.width = "50%"}
# 48-well
p3 = draw_cost_all(df = cost_all_48, n = 48, var = n_test_total, ylab = "Total number of assays (48-well plate)")
p3

# 96-well
p4 = draw_cost_all(df = cost_all_96, n = 96, var = n_test_total, ylab = "Total number of assays (96-well plate)")
p4
```

3. Visualization of labor cost

```{r, fig.show = "hold", out.width = "50%"}
# 48-well
p5 = draw_cost_all(df = cost_all_48, n = 48, var = n_pipette, ylab = "Total number of pipetting (48-well plate)")
p5

# 96-well
p6 = draw_cost_all(df = cost_all_96, n = 96, var = n_pipette, ylab = "Total number of pipetting (96-well plate)")
p6
```

```{r, eval = FALSE, echo= FALSE}
pdf(file = "Pooling Visualization 5.pdf")
  p1
  p2
  p3
  p4
  p5
  p6
dev.off()
```

