---
title: "Pooling paper 2"
author: "Xianbin Cheng"
date: "2/14/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Objective

  * Update `Pooling paper.Rmd` by using the Kolmogorov-Smirnov test to check the difference between simulated aflatoxin data and experimental aflatoxin data.
  
# Method

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
source("STD_simulation.R")
library(mc2d)
library(MASS)
library(EnvStats)
```

1. Remove observations whose aflatoxin concentration is below LOD. Eventually, there are 6 highs and 140 lows.

```{r, echo = TRUE}
# Experimental aflatoxin data are presented in ppb
Texas = read.csv(file = "Texas_Conc_Class_528obs_02_05_19.csv", header = TRUE, stringsAsFactors = FALSE, row.names = 1)

# Remove obs whose [FM] is below LOD
temp = Texas %>%
  dplyr::filter(!duplicated(x = Texas$AF.ppb.))
summary(as.factor(temp$AF_class))

# Summary
AF_H = subset(x = temp, subset = AF_class == "H", select = AF.ppb.) %>% unlist()
AF_L = subset(x = temp, subset = AF_class == "L", select = AF.ppb.) %>% unlist()
summary(AF_H)
summary(AF_L)
```

```{r, echo = FALSE}
a = ggplot(data = temp, aes(x = AF.ppb.)) +
  geom_histogram(aes(fill = AF_class), bins = 60) +
  scale_fill_discrete(name = "Single Kernel Aflatoxin Level", labels = c(">= 20 ppb", "< 20 ppb")) +
  labs(x = "Aflatoxin Concentration (ppb)", y = "Number of Kernels") +
  scale_x_log10(breaks = c(1e-2, 1e-1, 1, 1e1, 1e2, 1e3, 1e4, 1e5)) +
  theme_bw() +
  theme(legend.position = "top")
a
```

```{r, echo = TRUE}
set.seed(123)

fitdistr(x = AF_L, densfun = "lognormal")
fitdistr(x = AF_L/19.99, densfun = "beta", start = list(shape1 = 1, shape2 = 20), method = "BFGS")
# fitdistr(x = AF_L, densfun = rpert, start = list(mode = 1, shape = 20), min = 0, max = 19.99, method = "L-BFGS-B", lower = c(0.1, 1), upper = c(19, 100))

# PERT
neg1 = rpert(n = length(AF_L)*1000, min = 0, mode = 0.7, max = 19.99, shape = 80)
ks.test(x = neg1, y = AF_L)

# Beta
neg2 = 19.99* rbeta(n = length(AF_L)*1000, shape1 = 1.12, shape2 = 10.87)
ks.test(x = neg2, y = AF_L)

# Truncated Normal
neg3 = rlnormTrunc(n = length(AF_L)*1000, meanlog = 0.16, sdlog = 0.91, min = 0, max = 19.99)
ks.test(x = neg3, y = AF_L)

# Gamma
pos = rgamma_lim(n = length(AF_H)*1000, alpha = 2, mode = 40000, lb = 20, ub = NULL)
ks.test(x = pos, y = AF_H)

sim_data = data.frame(conc = c(pos, neg3))
wilcox.test(x = c(AF_H, AF_L), y = sim_data$conc)
ks.test(x = c(AF_H, AF_L), y = sim_data$conc)
```

# Conclusion

We can continue to use Wilcoxon rank sum test given that Wilcoxon rank sum test also investigates whether two independent samples were selected from populations having the same distribution.

# Appendix

```{r}
sessionInfo()
```

