---
title: 'Pooling Validation: 1D and 2D'
author: "Xianbin Cheng"
date: "2/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Objective

  We want to validate 1D and 2D pooling strategies by experiments on fumonisin-contaminated corn kernels.

# Method

```{r, echo = TRUE, warning = FALSE, message = FALSE}
library(tidyverse)
library(Hmisc)
library(mc2d)
library(EnvStats)
library(MASS)
source(file = "1D_pooling_simulation.R")
source(file = "2D_pooling_simulation.R")
source(file = "STD_simulation.R")
```

### 1. Experimental validation

```{r, echo = TRUE}
# sample size
n = 48
# positive threshold (ppm)
thresh = 1
```

```{r, echo = FALSE}
# Individual and pooled validation data are presented as ppb
FM_indiv = read.csv(file = "Validation_FM_indiv.csv", header = TRUE, stringsAsFactors = FALSE)
FM_pool = read.csv(file = "Validation_FM_pooled_1D2D.csv", header = TRUE, stringsAsFactors = FALSE)

result_indiv = FM_indiv %>%
  mutate(ID = str_split(string = .$Kernel_ID, pattern = "-", simplify = TRUE)[,2] %>% as.numeric(),
         row = rep(x = 1:6, each = 8), 
         column = rep(x = 1:8, times = 6), 
         FM_class = ifelse(test = .$FM_Conc >= thresh*1000, yes = 1, no = 0) %>% as.factor())

c_indiv = result_indiv$FM_Conc %>%
  matrix(data = ., nrow = 6, ncol = 8, byrow = TRUE) %>%
  as.vector()
pool_r = subset(x = FM_pool, subset = by == "row", select = FM_Conc, drop = TRUE)
pool_c = subset(x = FM_pool, subset = by == "column", select = FM_Conc, drop = TRUE)

result_pool = tibble(by = c(rep("row", length(pool_r)), rep("column", length(pool_c))),
                     conc = c(pool_r, pool_c),
                     ID = c(str_c(rep("R", length(pool_r)), seq_along(pool_r), sep = ""), str_c(rep("C", length(pool_c)), seq_along(pool_c), sep = "")))
```

```{r, echo = FALSE}
# a = ggplot(data = result_indiv) +
#   geom_col(aes(x = ID, y = FM_Conc)) +
#   geom_hline(yintercept = 1000, lty = 2) +
#   scale_y_log10() +
#   labs(x = "Single Kernel ID", y = "Fumonisin Concentration (ppb)") +
#   theme_bw()
# a

a = ggplot(data = result_indiv) +
  geom_tile(aes(x = column, y = row, fill = FM_class)) +
  scale_x_continuous(breaks = 1:8) +
  scale_y_continuous(breaks = 1:6) +
  scale_fill_discrete(name = "Single Kernel Fumonisin Level", c = c(0,1), l = c(90, 0), label = c("< 1 ppm", ">= 1 ppm")) +
  geom_vline(xintercept = seq(1.5, 7.5, 1), color = "white") +
  geom_hline(yintercept = seq(1.5, 5.5, 1), color = "white") +
  labs(x = "Column", y = "Row") +
  theme_classic() +
  theme(legend.position = "top")
a

b = ggplot(data = subset(x = result_pool, subset = by == "row"))+
  geom_col(aes(x = ID, y = conc/1000)) +
  geom_hline(yintercept = 1/length(pool_r), lty = 2) +
  scale_y_sqrt() +
  labs(x = "Row Pool ID", y = "Pooled Fumonisin Concentration (ppm)") +
  theme_bw()
b

c = ggplot(data = subset(x = result_pool, subset = by == "column"))+
  geom_col(aes(x = ID, y = conc/1000)) +
  geom_hline(yintercept = 1/length(pool_c), lty = 2) +
  scale_y_sqrt() +
  labs(x = "Column Pool ID", y = "Pooled Fumonisin Concentration (ppm)") +
  theme_bw()
c
```

```{r, echo = TRUE}
# In c(0, c_indiv), the 0 is a place holder for STD pooling.
metric_1d_r = calc_1d_metrics(n = n, thresh = 1000, conc = c(0, c_indiv), c_pool = pool_r, by = "row")
metric_1d_r

metric_1d_c = calc_1d_metrics(n = n, thresh = 1000, conc = c(0, c_indiv), c_pool = pool_c, by = "column")
metric_1d_c

metric_2d = calc_2d_metrics(conc = c(0, c_indiv), pool_r = pool_r, pool_c = pool_c, n = n, thresh = 1000)
metric_2d
```

### 2. Simulating fumonisin contamination.

  * We used the data from Texas corn 2017 (528 observations) and removed observations whose fumonisin concentration is below LOD. Eventually, we have 93 observations with 43 highs and 50 lows. 
  
  * We want to simulate fumonisin contamination in healthy kernels and contaminated kernels, assuming they both follow log normal distributions.
  
  * We used the maximum-likelihood method to estimate parameters and used the 2-sided Kolmogorov-Smirnov test to measure goodness of fit between the simulated data and experimental data.

```{r, echo = TRUE}
# Experimental fumonisin data are presented in ppm
Texas = read.csv(file = "Texas_Conc_Class_528obs_02_05_19.csv", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
Texas$FM_class[Texas$FM_class == "M"] = "H"

# Remove obs whose [FM] is below LOD
temp = Texas %>%
  dplyr::filter(!duplicated(x = Texas$FM.ppm.))
summary(as.factor(temp$FM_class))

# Summary
FM_H = subset(x = temp, subset = FM_class == "H", select = FM.ppm.) %>% unlist()
FM_L = subset(x = temp, subset = FM_class == "L", select = FM.ppm.) %>% unlist()
summary(FM_H)
summary(FM_L)
```

```{r, echo = FALSE}
ggplot(data = temp, aes(x = FM.ppm.)) +
  geom_histogram(aes(fill = FM_class), bins = 60) +
  scale_fill_discrete(name = "Single Kernel Fumonisin Level", labels = c(">= 1 ppm", "< 1 ppm")) +
  labs(x = "Fumonisin Concentration (ppm)", y = "Number of Kernels") +
  scale_x_log10() +
  theme_bw() +
  theme(legend.position = "top")
```

```{r, echo = TRUE}
set.seed(123)
fitdistr(x = FM_H, densfun = "lognormal")
fitdistr(x = FM_L, densfun = "lognormal")

prev = round(length(FM_H)/(length(c(FM_L, FM_H))), digits = 2)
n_total = 1e6

neg = rlnormTrunc(n = n_total*(1-prev), meanlog = -2.75, sdlog = 1.42, min = 0, max = 0.99)
pos = rlnormTrunc(n = n_total*prev, meanlog = 3.62, sdlog = 1.74, min = 1, max = Inf)
sim_data = data.frame(conc = c(pos, neg))

ks.test(x = temp$FM.ppm., y = sim_data$conc)
wilcox.test(x = temp$FM.ppm., y = sim_data$conc)
```

```{r, echo = FALSE}
d = ggplot(data = temp, aes(x = FM.ppm.)) +
  geom_histogram(aes(y = ..density..), bins = 60) +
  geom_density(data = sim_data, aes(x = conc), fill = "grey", alpha = 0.3) +
  scale_fill_discrete(name = "Single Kernel Fumonisin Level", labels = c(">= 1 ppm", "< 1 ppm")) +
  labs(x = "Fumonisin Concentration (ppm)", y = "Density") +
  scale_x_log10(breaks = c(0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  theme_bw() +
  theme(legend.position = "top")
d
```

### 3. Simulating pooling for fumonisin detection.

```{r, echo = TRUE}
set.seed(123)
sim_1d_row = tune_1d_n_pos(n_pos_vals = 17, n_iter = 10000, n = n, thresh = thresh, by = "row", tox = "FM")
sim_1d_col = tune_1d_n_pos(n_pos_vals = 17, n_iter = 10000, n = n, thresh = thresh, by = "column", tox = "FM")
sim_2d = tune_2d_n_pos(n_pos_vals = 17, n_iter = 10000, n = n, thresh = thresh, tox = "FM")
```

```{r}
f_vis = function(sim, experiment){
  sim2 = bind_cols(sim) %>%
    gather(data = ., key = "Metric", value = "Value", - n_pos) 

  temp = tibble(Metric = c("sensi", "speci"), Value = experiment)
  
  ggplot() +
    geom_boxplot(data = sim2, aes(x = as.factor(Metric), y = Value)) +
    geom_point(data = temp, aes(x = as.factor(Metric), y = Value),  size = 5, shape = 18) +
    scale_x_discrete(labels = c("Sensitivity", "Specificity")) +
    scale_y_continuous(breaks = seq(0, 1, 0.1)) +
    labs(x = NULL, y = "Metric value (48-well plate)") +
    coord_cartesian(ylim = c(0,1)) +
    theme_bw() +
    theme(axis.text.x = element_text(size = 12))
}
```

```{r, echo = TRUE}
e = f_vis(sim = sim_1d_row, experiment = metric_1d_r)
e
f = f_vis(sim = sim_1d_col, experiment = metric_1d_c)
f
g = f_vis(sim = sim_2d, experiment = metric_2d)
g
```

```{r}
my_summary = function(sim){
  
  sim2 = bind_cols(sim) %>%
    gather(data = ., key = "Metric", value = "Value", - n_pos) %>%
    dplyr::filter(Metric == "speci") 
  
  a = summary(sim2$Value)
  Q1 = a[2]
  Q3 = a[5]
  IQR = Q3 - Q1
  LIF = Q1 - 1.5*IQR
  UIF = Q3 + 1.5*IQR
  
  return(c(a, IQR = unlist(IQR), LIF = unlist(LIF), UIF = unlist(UIF)))
}

```

```{r, echo = TRUE}
my_summary(sim = sim_1d_row)
my_summary(sim = sim_1d_col)
my_summary(sim = sim_2d)
```

```{r, eval = FALSE}
pdf(file = "Pooling_validation_1D2D.pdf")
  a
  b
  c
  d
  e
  f
  g
dev.off()
```

```{r, echo = TRUE}
sessionInfo()
```

