---
title: 'STD: Simulation 2'
author: "Xianbin Cheng"
date: "December 13, 2018"
output: html_document
---

# Objective  

  1) We want to simulate the STD(48; 7; 2) and STD(96; 5; 3) pooling designs.
  
  2) We want to calculate the cost.
  
# Method  

1. Load libraries and necessary inputs. 

    * `n` = the number of kernels
    * `q_val` = the q value for STD pooling
    * `k_val` = the k value (number of layers) for STD pooling
    * `n_pos` = the number of positive kernels 
    * `thresh` = the aflatoxin level threshold (20 ppb)
    * `n_iter` = the number of iterations

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(raster)
library(mc2d)
source("STD_simulation.R")
```

```{r}
#n = 48
#q_val = 7
#k_val = 4
#n_pos = 3
thresh = 20
n_iter = 1000

STD_48 = read.csv("STD_48_7_2_1pos.csv", header = TRUE, row.name = 1, stringsAsFactors = FALSE)
STD_48_mat = read.csv("STD_48_7_2_1pos_mat.csv", header = TRUE, row.name = 1, stringsAsFactors = FALSE) %>%
  as.matrix()

STD_96 = read.csv("STD_96_5_3_1pos.csv", header = TRUE, row.name = 1, stringsAsFactors = FALSE) 
STD_96_mat = read.csv("STD_96_5_3_1pos_mat.csv", header = TRUE, row.name = 1, stringsAsFactors = FALSE) %>%
  as.matrix()
```

```{r, echo = FALSE}
draw_STD_2(STD_mat = STD_48_mat, n = 48, q = 7, k = 2)
draw_STD_2(STD_mat = STD_96_mat, n = 96, q = 5, k = 3)
```

```{r, echo = FALSE}
kable_styling(kable(x = STD_48, format = "html"))
kable_styling(kable(x = STD_96, format = "html"))
```

2. Define functions

```{r}
gen_elisa_af
gen_pool_af
rgamma_lim
calc_metrics
```

3. Iterate the simulation n times for each possible `n_pos`. `n_pos` has a range from 1 to (n-1). Calculate sensitivities and specificities.

```{r, eval = FALSE}
set.seed(123)
results_48 = tune_n_pos(n_pos_vals = 1:(48-1), n_iter = n_iter, n = 48, thresh = thresh, STD_mat = STD_48)
set.seed(123)
results_96 = tune_n_pos(n_pos_vals = 1:(96-1), n_iter = n_iter, n = 96, thresh = thresh, STD_mat = STD_96)

saveRDS(object = results_48, file = "STD_48_7_2_1000.rds")
saveRDS(object = results_96, file = "STD_96_5_3_1000.rds")
```

```{r, echo = FALSE}
results_48 = readRDS("STD_48_7_2_1000.rds")
results_96 = readRDS("STD_96_5_3_1000.rds")
```

```{r}
metrics_STD_48 = do.call(what = rbind.data.frame, args = results_48) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
metrics_STD_96 = do.call(what = rbind.data.frame, args = results_96) %>%
  gather(data = ., key = "Type", value = "Value", - n_pos)
```

4. Calculate the number of re-tests and number of pipetting for each `n_pos`. Assume that there's no error in the assay and we do not consider the scenario where a sample concentration exceeds the maximum limit of the ELISA assay. The number of pipetting times does not include the pipetting while performing the ELISA.

  `n(putative pos)` = TP + FP = sensitivity$\times$`n_pos` + (1 - specificity)$\times$(`n` - `n_pos`)

```{r}
cost_STD_48 = calc_STD_cost(data = results_48, n = 48, scheme = STD_48)
cost_STD_96 = calc_STD_cost(data = results_96, n = 96, scheme = STD_96)
```

# Results

1. Visualization. Medians with a range from 2.5th percentile to 97.5th percentile are shown here.

```{r, echo = FALSE, fig.keep = "high"}
# 48-well
draw_metrics(df = metrics_STD_48, n = 48, method = "median_hilow")

# 96-well
draw_metrics(df = metrics_STD_96, n = 96, method = "median_hilow")
```

2. Cost analysis

  1) The number of tests needed:

  The dashed line is the number of tests needed by individual testing (48 tests).

```{r}
# 48-well
draw_cost(df = cost_STD_48, n = 48, var = n_test_total, ylab = "The total number of tests needed")

# 96-well
draw_cost(df = cost_STD_96, n = 96, var = n_test_total, ylab = "The total number of tests needed")
```

  2) The number of pipetting needed:
  
```{r}
# 48-well
draw_cost(df = cost_STD_48, n = 48, var = n_pipette, ylab = "The number of transfers")

# 96-well
draw_cost(df = cost_STD_96, n = 96, var = n_pipette, ylab = "The number of transfers")
```
  
