---
title: "STD 2"
author: "Xianbin Cheng"
date: "February 7, 2019"
output: html_document
---

# Objective

  * Create STD pooling schemes for 48-well plates where prevalence is 0.02 (1 pos) with no pooling restriction.
  
  * Create STD pooling schemes for 96-well plates where prevalence is 0.01 (1 pos) with no pooling restriction.
  
# Method

1. Load necessary scripts and libraries.

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(binhf)
library(raster)
library(primes)
source("STD v4.R")
```

2. Set up basic parameters.

  * `n` = sample size
  * `d` = maximum number of positive samples expected
  * `E` = maximum allowable number of errors
  * `m` = maximum allowable number of individual samples in a pool

```{r}
#n = 48
d = 1
E = 0
#m = n
```

3. Run the STD generator.

```{r}
STD_generator
```

```{r}
STD_48_1pos = STD_generator(n = 48, d = d, E = E, m = 48)
STD_96_1pos = STD_generator(n = 96, d = d, E = E, m = 96)
```

# Result

```{r}
# 48 wells
STD_48_1pos$construction
draw_STD(data = STD_48_1pos, n = 48)

# 96 wells
STD_96_1pos$construction
draw_STD(data = STD_96_1pos, n = 96)
```

```{r, echo = FALSE, eval = FALSE}
write.csv(x = STD_48_1pos$table, file = "STD_48_7_2_1pos.csv", row.names = TRUE, col.names = TRUE)
write.csv(x = STD_96_1pos$table, file = "STD_96_5_3_1pos.csv", row.names = TRUE, col.names = TRUE)
write.csv(x = STD_48_1pos$matrix, file = "STD_48_7_2_1pos_mat.csv", row.names = TRUE, col.names = TRUE)
write.csv(x = STD_96_1pos$matrix, file = "STD_96_5_3_1pos_mat.csv", row.names = TRUE, col.names = TRUE)
```

